---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slurmtools

<!-- badges: start -->
[![R-CMD-check](https://github.com/A2-ai/slurmtools/actions/workflows/RunChecks.yaml/badge.svg)](https://github.com/A2-ai/slurmtools/actions/workflows/RunChecks.yaml)
<!-- badges: end -->

`slurmtools` is a collection of utility functions suitable for interacting with slurm and submitting nonmem jobs. There are three main functions of `slurmtools`

1. `submit_slurm_jobs` - submits a job to slurm via `sbatch`. The job is defined by a template file that is filled in during the call of this function
2. `get_slurm_jobs` - gives a tibble of currently runing jobs via `squeue`. 
3. `cancel_slurm_jobs` - cancels a running slurm job via `scancel`.

## Installation

You can install the development version of slurmtools from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pkg_install("a2-ai/slurmtools")
```

## Examples
This block sets up options used by slurmtools:
```{r setup}
nonmem = file.path(here::here(), "vignettes", "model", "nonmem")

options('slurmtools.submission_root' = file.path(nonmem, "submission-log"))
options('slurmtools.bbi_config_path' = file.path(nonmem, "bbi.yaml"))
options('slurmtools.slurm_job_template_path' = file.path(nonmem, 'slurm-job-bbi.tmpl'))

library(slurmtools)
```

```{r submit}
mod_number <- "1001"
mod <- bbr::read_model(file.path(nonmem, mod_number))

submit_slurm_job(mod, overwrite = TRUE)
```


```{r get}
knitr::kable(get_slurm_jobs(user = 'matthews'))
```
