---
title: "custom-alerts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{custom-alerts}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(slurmtools)
library(bbr)
library(here)

nonmem = file.path(here::here(), "vignettes", "model", "nonmem")
options('slurmtools.submission_root' = file.path(nonmem, "submission-log"))
```

## Submitting a NONMEM job with nmm

Instead of using bbi we can use nmm (NONMEM Monitor) which currently has
some additional functionality of sending slack notifications as well as
gradient monitoring.

We can update the template file accordingly:

``` slurm-job-nmm.tmpl
#!/bin/bash 
#SBATCH --job-name="{{job_name}}" 
#SBATCH --nodes=1 
#SBATCH --ntasks=1
#SBATCH --cpus-per-task={{ncpu}} 
#SBATCH --partition={{partition}}

{{nmm_exe_path}} -c {{config_toml_path}} run
```

default, `submit_nonmem_model` will provide `nmm_exe_path` and
`config_toml_path` to the template. Behind the scenes `nmm_exe_path` is
determined with `Sys.which("nmm")` which may or may not give you the
path to the nmm binary if it is on your path or not. We can inject the
`nmm_exe_path` like we did with `bbi_exe_path` and assume it's not on
our path.

Remember that error about the `config.toml` file not existing? Well this
is the reason. This file controls what `nmm` will monitor and where to
look for files and how to alert you. We'll use `generate_nmm_config()`
to create this file. First we can look at the documentation to see what
type of information we should pass to this function.![documentation for
generate_nmm_config()](data/images/generate_nmm_config_help.png)

```{r}
mod_number <- "1001"

if (file.exists(file.path(nonmem, paste0(mod_number, ".yaml")))) {
  mod <- bbr::read_model(file.path(nonmem, mod_number))
} else {
  mod <- bbr::new_model(file.path(nonmem, mod_number))
}
```

```{r}
slurmtools::generate_nmm_config(mod)
```

This generates the following toml file. Notice that alert is set to
'None', and email is empty. Since we're in vignettes we'll need to
update the watched_dir and output_dir.

Additionally, If we want to take advatnage of nmm's slack notifications
we'll have to add a few arguments to the generate_nmm_config function.

``` 1001.toml
model_number = '1001' 
files_to_track = [ 'lst', 'ext', 'grd' ] 
tmp_dir ='/tmp' 
watched_dir ='/cluster-data/user-homes/matthews/Packages/slurmtools/model/nonmem'
output_dir ='/cluster-data/user-homes/matthews/Packages/slurmtools/model/nonmem/in_progress'
poll_duration = 1 
alert = 'None' 
level = 'Debug' 
email = '' 
threads = 1
```

```{r}
slurmtools::generate_nmm_config( 
  mod, 
  alert = "slack", 
  email ="matthews@a2-ai.com", 
  watched_dir = "/cluster-data/user-homes/matthews/Packages/slurmtools/vignettes/model/nonmem",
  output_dir = "/cluster-data/user-homes/matthews/Packages/slurmtools/vignettes/model/nonmem/in_progress")
```

``` 1001.toml
model_number = '1001' 
files_to_track = [ 'lst', 'ext', 'grd' ] 
tmp_dir ='/tmp' 
watched_dir = '/cluster-data/user-homes/matthews/Packages/slurmtools/vignettes/model/nonmem'
output_dir = '/cluster-data/user-homes/matthews/Packages/slurmtools/vignettes/model/nonmem/in_progress'
poll_duration = 1 
alert = 'Slack' 
level = 'Debug' 
email ='matthews@a2-ai.com' 
threads = 1
```

We can now run `submit_nonmem_model` and get slack notifications about
our run.

```{r}
submission_nmm <- slurmtools::submit_nonmem_model( mod, overwrite =
TRUE, slurm_job_template_path = file.path(nonmem, "slurm-job-nmm.tmpl"),
slurm_template_opts = list(nmm_exe_path =
normalizePath("~/.local/bin/nmm")) )

submission_nmm
```

With `alert = 'Slack'` and `email` set in the config.toml file `nmm`
should send slack notifications directly to you when a NONMEM run starts
and it will reply to that message with notifications if any gradients
hit 0 and when the run finishes it checks if all -1E9 lines are present
in the .ext file and gives another message about any parameters that hit
0 gradient.![slack notifications from
nmm](data/images/nmm_slack_notifications.png)

```{r, include = FALSE}
#cancelling any running nonmem jobs
state <- slurmtools::get_slurm_jobs(user = "matthews")

if (any(state$job_state %in% c("RUNNING", "CONFIGURING"))) {
  for (job_id in state %>% dplyr::filter(job_state == "RUNNING") %>% dplyr::pull("job_id")) {
    processx::run("scancel", args = paste0(job_id))
  }
}

#removing generated files from running this vignette
nonmem <- file.path("model", "nonmem")

unlink(file.path(nonmem, "1001"), recursive = TRUE)
unlink(file.path(nonmem, "1001.yaml"))
unlink(file.path(nonmem, "1001.toml"))
unlink(file.path(nonmem, "submission-log"), recursive = TRUE) 
unlink(file.path(nonmem, "in_progress"), recursive = TRUE)
```
